### 2022-03-24 manuscript.tex
Update default.docx [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/e94f99edda419d16f3c4329fea505917908f8036.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/e94f99edda419d16f3c4329fea505917908f8036/checks
https://github.com/scherzerthesis/thesis/actions/runs/2034684001

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/22231633041f00c426f417c21e01890d62f0a00d/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/22231633041f00c426f417c21e01890d62f0a00d}{scherzerthesis/thesis@2223163}
on March 23, 2022.

@@

The 5-year survival rate for patients with lung cancer was 25\% in 2020 but varies depending on stage of disease at time of diagnosis (Siegel \emph{et al.}, 2021).Like other solid cancers, lung cancers are most deadly after primary tumors have metastaized to other organ systems like the liver, kidney, bone, or nervous system (Matsunaga and Shida, 1971). Lung cancer patients with no local or distant metastasis typically have a 5-year survival percentage of approximately 40\% compared to approximately 5\% with distant metastasis{[}Woodard \emph{et al.}; 27740970{]}. Ultimately, the cause of death of many lung cancer patients include primary lung tumor burden, infection, pulmonary embolism or hemorrhage, or complications of metastatic dissemination(Nichols \emph{et al.}, 2012). Although patient survival has improved due to improved targeted and immune therapies, the still poor prognosis reflects a need to better understand the molecular mechanisms underlying lung adenocarcinoma initiation, progression, maintenance and response to targeted- or immune-therapy.

@@

\leavevmode\vadjust pre{\hypertarget{ref-gY2NonCA}{}}%
Siegel,R.L. \emph{et al.} (2021) \href{https://doi.org/10.3322/caac.21654}{Cancer Statistics, 2021}. \emph{CA A Cancer J. Clin.}, \textbf{71}, 7--33.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/e94f99edda419d16f3c4329fea505917908f8036/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/e94f99edda419d16f3c4329fea505917908f8036}{scherzerthesis/thesis@e94f99e}
on March 24, 2022.

@@

The 5-year survival rate for patients with lung cancer was 25\% in 2020 but varies depending on stage of disease at time of diagnosis (\textbf{doi:10.3322/caac.21654?}).Like other solid cancers, lung cancers are most deadly after primary tumors have metastaized to other organ systems like the liver, kidney, bone, or nervous system (Matsunaga and Shida, 1971). Lung cancer patients with no local or distant metastasis typically have a 5-year survival percentage of approximately 40\% compared to approximately 5\% with distant metastasis{[}Woodard \emph{et al.}; 27740970{]}. Ultimately, the cause of death of many lung cancer patients include primary lung tumor burden, infection, pulmonary embolism or hemorrhage, or complications of metastatic dissemination(Nichols \emph{et al.}, 2012). Although patient survival has improved due to improved targeted and immune therapies, the still poor prognosis reflects a need to better understand the molecular mechanisms underlying lung adenocarcinoma initiation, progression, maintenance and response to targeted- or immune-therapy.

@@
